\documentclass[Main]{subfiles}

\begin{document}

\section{Scenario}


\subsection{Data types}
Data types are not discussed in this document, and offer little to no inside of how to handle data.
It is stated the course has groups, filled with joiners and each course is set on a specific date.
Each joiner must wear a badge created by an employee and the joiners of a course should be printable.
All data goes through the system and are mostly collected from the Personal Information System (PIS) and in few cases created on-the-fly.
\\
\\
Most of these data types are easy to describe, both in structure and relation.



\subsection{Incorrect functionality scenario}
In writing the specifications there are unanswered questions and holes in the scenarios for handling the clients of the system.




\paragraph{Input and output}
\begin{itemize}
\item \textbf{ID 20140301-094900}: What is the optimal group size? 
Who decides how many groups should be created?

\item \textbf{ID 20140301-095600}: Should the same-office joiners still be as split as possible? Or will anything go here?

\end{itemize}




\paragraph{System events}




\paragraph{Invariant properties}

Hard to say -- not enough data!



\paragraph{Ambiguities and missing functionality}
\begin{itemize}
\item When are the events created? 

\item Who can create an event?

\item Will badges be printed when a user signs in to a course or beforehand?
\fxnote{Should this be on the list?}

\item Is the authentication related to the joiner's login at work?

\item How are unexpected participants handled? Room, group?

\item Who will host the server?

\item Who will handle support for the system?

\item \dots
\end{itemize}






\end{document}