\documentclass[Main]{subfiles}
\begin{document}

\section{Maintenance}

\begin{DynTable}{Requirements for defect removal}
\Dyn{1}
{\textbf{Fractile}. The response times specified below must apply in almost all cases.}
{$\underline{\quad}$\% of the response times must be within the limits. 
(The customer expects 95\%.)}
{}


\Dyn{2}
{The supplier keeps a log of reported defects as well as change requests.}
{}
{}

\Dyn{3}
{For all reported defects, the supplier quickly decides whether the defect is business critical, possible to circumvent temporarily, or possible to circumvent permanently (i.e. reject).}
{In the period from 8:00 to 18:00 on weekdays, the supplier completes the assessment within $\underline{\quad}$ hours. \\
(The customer expects 3 hours.)}
{}

\Dyn{4}
{Business-critical defects are removed quickly. }
{Business-critical defects are removed within $\underline{\quad}$hours. 
(The customer expects 24 hours.)}
{}

\Dyn{5}
{Customer and supplier meet regularly to check the defect assessments, and to decide what to repair or change, and what it will cost.}
{The parties meet every $\underline{\quad}$ months.\\
(The customer expects monthly meetings.)}
{}


\end{DynTable}

\begin{DynTable}{Requirements for system improvement}
\Dyn{6}
{The supplier installs new versions and releases of the delivered software without unduly delay.}
{Installation takes place within $\underline{\quad}$ days after release of the new version.\\
(The customer expects 30 days.)}
{}

\Dyn{7}
{Within a period of 3 years, the supplier must offer changes at a fixed price per Function Point or COSMIC point.}
{The price per Function Point / COSMIC point is $\underline{\quad}$.}
{}

\Dyn{8}
{Disagreement on the Function Point / COSMIC point calculation must be resolved by}
{\dots}
{}

\end{DynTable}


\end{document}