\documentclass[Main]{subfiles}
\begin{document}

\section{Business goals}
The customer's reason to acquire the system is to reach some business goals. 
The customer expects that the system contributes to the goals as stated below. 
The supplier can rarely reach the goals alone. Customer contribution is needed too. 
This means that the goals are not requirements to the supplier. 
They are shown in a table only to provide overview. 
\\
\\
All goals are important and the sooner they can be met, the better. 
Some goals are crucial to meet at a specific date, for instance for business or legal reasons. 
Such deadlines are shown in the table.

\begin{GoalTable}

\Goal
{A student uploads a handin and the system distribute it for review on its own.}
{The system shall make distributing handins easy.}
{Support task \ref{sec:SubmitHandin} (Submit handin).}
{}

\Goal
{When a student shall review other student's handins, the handins are sent to them.}
{The system shall make reviewing overview better for the student}
{Support task \ref{sec:SubmitReview} (Submit Review).}
{}

\Goal
{Informs on deadline which students exceed the deadline.}
{Provide a better overview of who exceed deadlines for handins and review for the teacher.}
{Support task \ref{sec:ManageGroupSubmissions}.}
{}

\Goal
{Provides an over\-view of reviews marked as "not ok" for the teacher.}
{The teacher can see which reviews are marked "not ok".}
{Support task \ref{sec:ManageGroupSubmissions}.}
{}

\end{GoalTable}
















\end{document}