\documentclass[Main]{subfiles}

\begin{document}

\section{Comparison of specification techniques}
%This part shall contain a comparison of pros and cons with different specification techniques and a reflection of your own experience in using different kinds of techniques (around 2 pages).

When writing specifications, different techniques can be used.
In the bachelor degree of this education the traditional standard of making use cases has been used and favored over all else.
It has worked nicely for multiple projects and each time has been a new challenge with new obtained knowledge of how to create a better specifications.

In TISPIT a new method was introduced  which had a very different approach to dealing with a systems specification and design.
Group 6 was first introduced to this in an article in handin 2, \parencite[]{HI2}, when reading Søren Lauesen's idea of Task-Description, \parencite[]{Task}.

The paper explained a second way of dealing with user's needs and why this approach would be easier to use, versus the old way with use cases.
The main argument of this article was, that using this method can save a lot of time and according to another article, \parencite[]{Task2}, a quick survey showed that 45 \% of asked teams used this (or similar methods) in 2012 which only underlines, that this is a growing way of addressing customers' needs today.
\\
\\
Assuming the claims made in Søren Lauesen's idea of Task-Description \parencite[]{Task} is true -- doing things faster is normally a good thing, assuming the outcome is as good as the slower approach.
But it is not only a matter of speed -- it is a matter of understanding what is to be done in the specification.

In the traditional view, use cases are created.
They state who interact with the system (hardware and software), pre- and postconditions, what scenarios will happen step by step, each step specifying which actor performs the step.
This approach is great for specifying scenarios fitting that pattern. However, such a description may not be easily understandable by the customer  if the task to be performed does not map well to use cases. 

In the Task-description approach the use cases are replaced by tasks the customer can understand from the customer's daily routines.
This could be \textit{check a hotel guest in to the system} and then describe what the customer already know, step by step, with small subtasks.
Now the customer can read and understand what is to become with the task, what he is paying for and the task will be completed.
How it should be executed is not specified yet.
With the same example it could be a guest coming to the counter asking an employee to check in the guest or it could be a small screen with clear instructions the guest could check him self in with.
The outcome would be exactly the same -- only the execution would be different. Task descriptions also allow for the customers current problem to be stated along with the relevant task, thus making the context more understandable for a supplier.
\\
\\
If the contractor doesn't need to sit with a team of software engineers and almost design the system before it is approved, the contractor can just write what the customer wants, specify step by step of each task, let the customer approve it and then sit down with the engineers to design the system, thus saving time and money.

Tasks will specify what the user \textit{and} the system should accomplish together.
This can be challenging to get used to for engineers who only have worked with the traditional way of writing specifications.

Task-descriptions map closely to every task performed by the user. This means that task-descriptions are more likely to be correct than use case descriptions. This allows defects to be detected earlier in the process.
\\
\\
To support the informal specification methods like use cases and task descriptions, formal methods provide means for specifying and analysing systems using mathematical entities and concepts. While informal methods provide context for the reader, and generally more readable specifications, the formal methods offer precise and unambiguous methods to describe a system. Using formal methods does not ensure the completeness of a system, furthermore, using formal methods for trivial systems will most likely not result an advantage over informal methods. 

Using most formal methods requires mathematical knowledge, thus resulting in a steeper learning curve, which was also the case with the formal specification language VDM-SL used in this course during handin 3 \parencite[]{HI3}. This means that formal methods are of limited use when discussing requirements with customers, however modelling essential parts of a system allows certain system properties to be verified. Using a formal method provides an unambiguous and consistent way to convey requirements, which does not exist when relying on natural language as informal methods do.



\end{document}